Entropy-SGD: Biasing Gradient Descent Into Wide Valleys

### 2017-01-12 doc/rebuttal.txt

One could argue that accuracy in the approximation of HVP does not matter in practice for purposes of training; what matters is only the local curvature at a scale commensurate with the typical weight updates. The perturbation vector for computing HVPs using back-props thus needs to be chosen carefully. If so, indeed, approximate computation of HVP can be considered cheap.

[LSP93] LeCun, Yann, Patrice Y. Simard, and Barak Pearlmutter. "Automatic learning rate maximization by on-line estimation of the Hessian’s eigenvectors." NIPS (1993).
[P94] Pearlmutter, Barak A. "Fast exact multiplication by the Hessian." Neural computation 6.1 (1994): 147-160.
[M10] Martens, James. "Deep learning via Hessian-free optimization." ICML (2010).

-----------------------------------------------------------------------

--------------------
Area chair:

>> You should make the connections clearer and more explicit
We have updated the paper with the above discussion about SVI and experiments comparing with SGLD in Appendix C. As our previous comment shows, it'd be inaccurate to term local entropy as "SVI with a moving prior" since the latter is not rigorously defined, the resemblance is quite conceptual in nature.

>> change x-axis for error curves
We have updated the experiments in the paper and now plot all error curves against the "effective number of epochs", i.e., the number of epochs for Entropy-SGD is multiplied by L (we set L=1 for SGD/Adam). Note that this is proportional to the number of back-props. Please see the "updates to the paper" comment above for more details.

>> Exact HVP is easy to compute
The comment regarding [P94] above discusses this. Computing the exact HVP requires averaging over the entire dataset, i.e., ~4x the complexity of one epoch, which is expensive.

---------------------------
REBUTTAL

### 2017-01-13 doc/rebuttal.txt

[LSP93] LeCun, Yann, Patrice Y. Simard, and Barak Pearlmutter. "Automatic learning rate maximization by on-line estimation of the Hessian’s eigenvectors." NIPS (1993).
[P94] Pearlmutter, Barak A. "Fast exact multiplication by the Hessian." Neural computation 6.1 (1994): 147-160.
[M10] Martens, James. "Deep learning via Hessian-free optimization." ICML (2010).

-----------------------------------------------------------------------

--------------------
Area chair:

>> You should make the connections clearer and more explicit
We have updated the paper to include the above discussion about SVI and added experiments comparing with SGLD in Appendix C. As our previous comment shows, it'd be inaccurate to term local entropy as "SVI with a moving prior" since the latter is not rigorously defined, their resemblance is quite conceptual in nature.

@@

>> change x-axis for error curves
We have updated the experiments in the paper and now plot all error curves against the "effective number of epochs", i.e., the number of epochs for Entropy-SGD is multiplied by L (we set L=1 for SGD/Adam). Note that this is proportional to the number of back-props. Please see the "updates to the paper" comment above for more details.

(maybe can skip this, it is not relevant in light of faster expts.)
>> Exact HVP is easy to compute
The comment regarding [P94] above discusses this. Computing the exact HVP requires averaging over the entire dataset, i.e., ~4x the complexity of one epoch, which is expensive.

---------------------------
MAIN REBUTTAL

We thank the reviewers and the area chair for their insightful feedback. We have incorporated all comments into our current draft. We first discuss the updates to the paper and address common questions raised by the reviewers. We have also posted individual comments to the reviewers to address specific questions.

@@

Updates
-------

a) We have updated the experimental section of the paper with new experiments on MNIST, CIFAR-10 and two datasets on RNNs (PTB and char-LSTM). We also modified the algorithm to introduce a technique called "scoping", this increases the scoping parameter \gamma as training progresses instead of fixing it (Sec. 4.3). As a result of this, we can now train all our networks with only the local entropy loss instead of treating it as a regularizer (Eqn. 6).

For a fair comparison of the training time, we now plot the error curves in Figs. 4, 5 and 6 against the "effective number of epochs", i.e., the number of epochs of Entropy-SGD is multiplied by the number of Langevin iterations L (we set L=1 for SGD/Adam). Thus the x-axis is thus a direct measure of the wall-clock time agnostic to the underlying implementation and is proportional to the number of back-props as suggested.

We obtain significant speed-ups with respect to our earlier results due to scoping and the wall-clock training time for all our networks with Entropy-SGD is now comparable to SGD/Adam. In fact, Entropy-SGD is twice as fast as SGD on our experiments on RNNs and also obtains a better generalization error (cf. Fig. 6). The acceleration for CNNs on MNIST and CIFAR-10 is about 20%.

@@

b) Improved exposition of the algorithm in Sec. 4.2 and discussion of experiments in Sec. 5.3, 5.4 that includes intuition for hyper-parameter tuning.

c) Appendix C discusses the possible connections to variational inference (this is the same material as the discussion with the AC below). Sec. C.1 presents a comparison of local entropy and SGLD. We note here that our results using Entropy-SGD for both CNNs and RNNs are much better than SGLD in significantly smaller (~3x) wall-clock times.

@@

Response to the reviewers:
-------------------------

a) smoothing of the original loss vs. local entropy
We discuss this in detail in the related work in Sec. 2 and Appendix C. While smoothing the original loss function using convolutions or averaging gradient over perturbations of weights reduces the ruggedness of the energy landscape, it does not help with sharp, narrow valleys. Local entropy introduces a measure that focuses on wide local minima in the energy landscape (cf. Fig. 2 which has a "global" minimum at a wide valley); this is the primary reason for its efficacy. Smoothing the loss function can also, for instance, generate an artificial local minimum between two close by sharp valleys which is detrimental to generalization.

b) unrealistic eigenvalue assumption in Sec. 4.3
We have clarified this point in Remark 4. Our analysis employs an assumption that the Hessian \nabla^2 f(x) does not have eigenvalues in the set [-2\gamma-c, c]. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian in Fig. 1 has a large fraction of its eigenvalues almost zero. Let us note though that Fig. 1 is plotted at a local minimum, the eigenspectrum is less sparse in the beginning of training, but quite similar to Fig. 1.

The bound on uniform stability in Thm. 3 by Hardt et al. assumes global conditions on the smoothness of the loss function; one imagines that Eqn. 9 remains qualitatively the same (with respect to the number of training iterations in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption requires a dynamical analysis of SGD and seems out of reach currently.

### 2017-01-13 doc/chaudhari.choromanska.ea.iclr17.tex
just polishing, minor updates

\todo{
Closer to the subject of this paper are results by~\citet{baldassi2015subdominant,baldassi2016unreasonable,baldassi2016multilevel} who show that the energy landscape of shallow networks with discrete weights is characterized by an exponential number of isolated minima and few very dense regions with lots of local minima close to each other. These dense local minima can be shown to generalize well for random input data; more importantly, they are also accessible by efficient algorithms using a novel measure called ``robust ensemble'' that amplifies the weight of such dense regions. The authors use belief propagation to estimate local entropy for simpler models considered there. A related work in this context is EASGD~\citep{zhang2015deep} which trains multiple deep networks in parallel and modulates the distance of each worker from the ensemble average. Such an ensemble training procedure enables improved generalization by ensuring that different workers land in the same wide valley and indeed, it turns out to be closely related to the replica theoretic analysis of~\citep{baldassi2016unreasonable}.

@@

\pc{Motivated by the same final goal, viz., flat local minima, the authors in~\citet{hochreiter1997flat} introduce hard constraints on the training loss and the width of local minima and show using the Gibbs formalism~\citep{haussler1997mutual} that this leads to improved generalization. As the authors discuss, the effect of hyper-parameters for the constraints is intricately tied together and they are difficult to choose even for small problems. Our local entropy based objective naturally balances the energetic term (training loss) and the entropic term (width of the valley) and also results in a more scalable algorithm. The ``scope'' $\g$ affords more control on the optimization process than hard constraints and as we discuss in Sec.~\ref{s:scoping}, this also provides significant computational advantages. The Gibbs formalism used in the analysis of~\citet{hochreiter1997flat} is however a very promising direction to understanding generalization in deep networks in the context of this paper.}{While the motivations are exactly the same, the similarities with their formulation are only conceptual in nature, e.g., in a flat minimum, the local entropy is a direct measure of the width of the valley which is similar to their usage of Hessian. The Gibbs variant to averaging in weight space (Eqn. 33, pg. 22 of [HS97]) is similar to the averaging in Eqn. 7 of our paper.}

Another related area is homotopy continuation methods that convolve the loss function to solve sequentially refined optimization problems~\citep{allgower2012numerical,mobahi2015link} or methods that perturb the weights or activations to average the gradient~\citep{gulcehre2016mollifying} with an aim to smooth the rugged energy landscape. Such a smoothing is however different from local entropy. For instance, the latter places more weight on wide local minima even if they are much shallower than the global minimum (cf. Fig.~\ref{fig:entropyfig}) which cannot be obtained by smoothing. In fact, smoothing can introduce an artifical minimum between two sharp valleys connected by a high energy barrier which is detrimental to generalization. Please refer to Sec.~\ref{s:app:connection_variational} for a more elaborate discussion. In order to be effective, continuation techniques also require that minimizers of successively smaller convolutions of the loss function lie close to each other~\citep{DBLP:conf/icml/HazanLS16}; it is not clear whether this is true for deep networks. Local entropy exploits wide minima which have been shown to exist in a variety of learning problems~\citep{monasson1995weight,cocco1996analytical}; our experiments on the eigenspectrum of the Hessian are a step to showing the existence of such wide minima in modern deep networks.

@@

\begin{definition}[Local entropy]
\label{def:local_entropy}
The local free entropy of the Gibbs distribution in~\eqref{eq:gibbs_original}, colloquially called ``local entropy'' in the sequel and denoted by $F(x, \g)$, is defined as the log-partition function of modified Gibbs distribution~\eqref{eq:gibbs_modified}, i.e.,
\begin{align}
    F(x, \g) &= \log Z_{x, 1, \g} \notag\\
    &= \log \int_{x'}\ \exp \Big(-f(x') - \f{\g}{2}\ \norm{x-x'}^2_2 \Big)\ dx'.
    \label{eq:local_entropy}
\end{align}
\end{definition}
The parameter $\g$ is used to focus the modified Gibbs distribution upon a local neighborhood of $x$ and we call it a ``scope'' henceforth. Fig.~\ref{fig:entropyfig} shows the negative local entropy $-F(x, \g)$ for the original energy landscape. Note that $-F(x, \g)$ has a \emph{global} minimum near $x_{\textrm{robust}}$ which is exactly what we want; we expect $x_{\textrm{robust}}$ to be more robust than $x_{\textrm{non-robust}}$ to perturbations of data or parameters and thus generalize well.

@@

The scoping parameter $\g$ is fixed in Alg.~\ref{alg:entropysgd}. For large values of $\g$, the SGLD updates happen in a small neighborhood of the current parameters $x$ while low values of $\g$ allow the inner SGLD to explore further away from $x$. A ``reverse-annealing'' of the scope $\g$, i.e. increasing $\g$ as training progresses, thus has the effect of exploring the energy landscape on progressively finer scales. This process is called ``scoping''~\citep{baldassi2016unreasonable} and use a simple exponential schedule given by
$$
    \g(t) = \g_0\ \rbrac{1 + \g_1}^t;
$$
for the $t^{\trm{th}}$ parameter update. We have experimented with linear, quadratic and bounded exponential ($\g_0 \rbrac{1 - e^{-\tau t}}$) scoping schedules and obtained qualitatively similar results.

@@

\begin{remark}
The above analysis hinges upon an assumption that the Hessian $\nabla^2 f(x)$ does not have eigenvalues in the set $[-2\g-c, c]$ for a constant $c > 0$. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian at a local minimum in Fig.~\ref{fig:lenet_hessian} has a large fraction of its eigenvalues almost zero. Let us however remark that the bound on uniform stability in Thm.~\ref{thm:generalization_bound_nonconvex} by~\citet{hardt2015train} assumes global conditions on the smoothness of the loss function; one imagines that Eqn.~\ref{eq:stability_bound} remains qualitatively the same (with respect to $T$ in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption would require a dynamical analysis of SGD and seems out of reach of the current literature.
\end{remark}

@@

For both these networks, we train $\entropysgd$ for $5$ epochs with $L = 20$ and reduce the dropout probability ($0.15$ for $\mnistfc$ and $0.25$ for $\lenet$). The learning rate of the SGLD updates is fixed to $\eta' = 0.1$ while the outer loop's learning rate is set to $\eta=1$ and drops by a factor of $10$ after the second epoch; we use Nesterov's momentum for both the loops. The thermal noise in SGLD updates (Line 5 of Alg.~\ref{alg:entropysgd}) is set to $10^{-3}$. We use an exponentially increasing value of $\g$ for scoping, the initial value of the scope is set to $\g = 10^{-4}$ and this increases by a factor of $1.001$ after each parameter update. The results in Fig.~\ref{fig:mnistfc_test} and Fig.~\ref{fig:lenet_test} show that $\entropysgd$ obtains a comparable generalization error: $1.37 \pm 0.03 \%$ and $0.50 \pm 0.01 \%$, for $\mnistfc$ and $\lenet$ respectively.

@@

As noted in Sec.~\ref{ss:alg}, we can easily wrap Alg.~\ref{alg:entropysgd} inside other variants of SGD such as Adam; this involves simply substituting the local entropy gradient in place of the usual back-propagated gradient. For this experiment, we constructed $\entropyadam$ which is equivalent to Adam with the local entropy gradient (which is computed via SGLD). We run $\entropyadam$ for $5$ epochs with $L = 5$ and a fixed $\g = 0.01$ with an initial learning rate of $0.01$ that decreases by a factor of $2$ at each epoch. Note that this again results in only $25$ effective epochs, i.e. half as much wall-clock time as Adam. We obtain a validation perplexity of $1.213 \pm 0.007$ and a test perplexity of $1.217 \pm 0.005$ over $4$ independent runs which is better than the baseline. We plot the error curves in Fig.~\ref{fig:char_valid} for this experiment.

@@

After a hyper-parameter search, we obtained a test error on $\lenet$ of $0.63 \pm 0.1\%$ after $300$ epochs and $9.89 \pm 0.11\%$ on $\allcnn$ after $500$ epochs. Even if one were to disregard the slow convergence of SGLD, its generalization error is much worse than our experimental results; we get $0.50 \pm 0.01 \%$ on $\lenet$ and $7.81 \pm 0.09 \%$ on $\allcnn$. For comparison, the authors in~\citet{chen2015bridging} report $0.71\%$ error on MNIST on a slightly larger network. Our results with local entropy on RNNs are much better than those reported in~\citet{gan2016scalable} for SGLD. On the PTB dataset, we obtain a test perplexity of $77.656 \pm 0.171$ vs. $94.03$ for the same model whereas we obtain a test perplexity of $1.213 \pm 0.007$ vs. $1.3375$ for $\charlstm$ on the War and Peace dataset.

Training Bayesian deep networks with SGLD, or other more sophisticated algorithms such as SGHMC~\citep{chen2014stochastic,neal2011mcmc} is difficult and the lack of such results in the literature corroborates our experimental results. Roughly speaking, local entropy is so effective because it operates on a transformation of the energy landscape that exploits local entropic effects. Conventional MCMC techniques such as SGLD or Nose'-Hoover thermostats~\citep{ding2014bayesian} can only trade energy for entropy via the temperature parameter which does not allow the direct use of the geometric information of the energy landscape and does not help with narrow minima.

>>>>

\todo{
Closer to the subject of this paper are results by~\citet{baldassi2015subdominant,baldassi2016unreasonable,baldassi2016multilevel} who show that the energy landscape of shallow networks with discrete weights is characterized by an exponential number of isolated minima and few very dense regions with lots of local minima close to each other. These dense local minima can be shown to generalize well for random input data; more importantly, they are also accessible by efficient algorithms using a novel measure called ``robust ensemble'' that amplifies the weight of such dense regions. The authors use belief propagation to estimate local entropy for simpler models considered there. A related work in this context is EASGD~\citep{zhang2015deep} which trains multiple deep networks in parallel and modulates the distance of each worker from the ensemble average. Such an ensemble training procedure enables improved generalization by ensuring that different workers land in the same wide valley and indeed, it turns out to be closely related to the replica theoretic analysis of~\citet{baldassi2016unreasonable}.

@@

Motivated by the same final goal, viz. flat local minima, the authors in~\citet{hochreiter1997flat} introduce hard constraints on the training loss and the width of local minima and show using the Gibbs formalism~\citep{haussler1997mutual} that this leads to improved generalization. As the authors discuss, the effect of hyper-parameters for the constraints is intricately tied together and they are difficult to choose even for small problems. Our local entropy based objective naturally balances the energetic term (training loss) and the entropic term (width of the valley). The ``scope'' $\g$ affords more control on the optimization process than hard constraints and as we discuss in Sec.~\ref{s:scoping}, this also provides significant computational advantages. Among other conceptual similarities with our work, let us note that local entropy in a flat valley is a direct measure of the width of the valley which is similar to their usage of Hessian while the Gibbs variant to averaging in weight space (Eqn. 33 of~\citet{hochreiter1997flat}) is similar to our Eqn.~\eqref{eq:entropysgd_grad}. Indeed, Gibbs formalism used in the analysis of~\citet{hochreiter1997flat} is a very promising direction to understanding generalization in deep networks~\citep{zhang2016understanding}.

Homotopy continuation methods convolve the loss function to solve sequentially refined optimization problems~\citep{allgower2012numerical,mobahi2015link} or methods that perturb the weights or activations to average the gradient~\citep{gulcehre2016mollifying} with an aim to smooth the rugged energy landscape. Such a smoothing is however different from local entropy. For instance, the latter places more weight on wide local minima even if they are much shallower than the global minimum (cf. Fig.~\ref{fig:entropyfig}); this effect cannot be obtained by smoothing. In fact, smoothing can introduce an artificial minimum between two close by sharp valleys which is detrimental to generalization. Please refer to Sec.~\ref{s:app:connection_variational} for a more elaborate discussion. In order to be effective, continuation techniques also require that minimizers of successively smaller convolutions of the loss function lie close to each other~\citep{DBLP:conf/icml/HazanLS16}; it is not clear whether this is true for deep networks. \todo{Local entropy, on the other hand, exploits wide minima which have been shown to exist in a variety of learning problems~\citep{monasson1995weight,cocco1996analytical}, shallow neural networks in particular.}

@@

\begin{definition}[\textbf{Local entropy}]
\label{def:local_entropy}
The local free entropy of the Gibbs distribution in~\eqref{eq:gibbs_original}, colloquially called ``local entropy'' in the sequel and denoted by $F(x, \g)$, is defined as the log-partition function of modified Gibbs distribution~\eqref{eq:gibbs_modified}, i.e.,
\begin{align}
    F(x, \g) &= \log Z_{x, 1, \g} \notag\\
    &= \log \int_{x'}\ \exp \Big(-f(x') - \f{\g}{2}\ \norm{x-x'}^2_2 \Big)\ dx'.
    \label{eq:local_entropy}
\end{align}
\end{definition}
The parameter $\g$ is used to focus the modified Gibbs distribution upon a local neighborhood of $x$ and we call it a ``scope'' henceforth.

\paragraph{Effect on the energy landscape:}
Fig.~\ref{fig:entropyfig} shows the negative local entropy $-F(x, \g)$ for the original energy landscape. We expect $x_{\textrm{robust}}$ to be more robust than $x_{\textrm{non-robust}}$ to perturbations of data or parameters and thus generalize well and indeed the negative local entropy in Fig.~\ref{fig:entropyfig} has a \textbf{global} minimum near $x_{\textrm{robust}}$. For low values of $\g$, the energy landscape is significantly smoother and still maintains our this desired characteristic. As $\g$ increases, the local entropy energy landscape gets closer to the original energy landscape and they become equivalent at $\g \to \infty$. On the other hand, for very small values of $\g$, the local entropy energy landscape is almost uniform.

@@

The scoping parameter $\g$ is fixed in Alg.~\ref{alg:entropysgd}. For large values of $\g$, the SGLD updates happen in a small neighborhood of the current parameters $x$ while low values of $\g$ allow the inner SGLD to explore further away from $x$. In the context of the discussion in Sec.~\ref{s:local_entropy}, a ``reverse-annealing'' of the scope $\g$, i.e. increasing $\g$ as training progresses has the effect of exploring the energy landscape on progressively finer scales. We call this process ``scoping'' which is similar to that of~\citet{baldassi2016unreasonable} and use a simple exponential schedule given by
$$
    \g(t) = \g_0\ \rbrac{1 + \g_1}^t;
$$
for the $t^{\trm{th}}$ parameter update. We have experimented with linear, quadratic and bounded exponential ($\g_0 \rbrac{1 - e^{-\tau t}}$) scoping schedules and obtained qualitatively similar results.

@@

\begin{remark}
The above analysis hinges upon an assumption that the Hessian $\nabla^2 f(x)$ does not have eigenvalues in the set $[-2\g-c, c]$ for a constant $c > 0$. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian at a local minimum in Fig.~\ref{fig:lenet_hessian} has a large fraction of its eigenvalues almost zero. Let us however remark that the bound on uniform stability in Thm.~\ref{thm:generalization_bound_nonconvex} by~\citet{hardt2015train} assumes global conditions on the smoothness of the loss function; one imagines that Eqn.~\ref{eq:stability_bound} remains qualitatively the same (with respect to $T$ in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption would require a dynamical analysis of SGD and seems out of reach currently.
\end{remark}

@@

For both these networks, we train $\entropysgd$ for $5$ epochs with $L = 20$ and reduce the dropout probability ($0.15$ for $\mnistfc$ and $0.25$ for $\lenet$). The learning rate of the SGLD updates is fixed to $\eta' = 0.1$ while the outer loop's learning rate is set to $\eta=1$ and drops by a factor of $10$ after the second epoch; we use Nesterov's momentum for both the loops. The thermal noise in SGLD updates (Line 5 of Alg.~\ref{alg:entropysgd}) is set to $10^{-3}$. We use an exponentially increasing value of $\g$ for scoping, the initial value of the scope is set to $\g = 10^{-4}$ and this increases by a factor of $1.001$ after each parameter update. The results in Fig.~\ref{fig:mnistfc_test} and Fig.~\ref{fig:lenet_test} show that $\entropysgd$ obtains a comparable generalization error: $1.37 \pm 0.03 \%$ and $0.50 \pm 0.01 \%$, for $\mnistfc$ and $\lenet$ respectively. While $\entropysgd$ trains slightly faster in wall-clock time for $\lenet$; it is marginally slower for $\mnistfc$ which is a small network and trains in about two minutes anyway.

@@

As noted in Sec.~\ref{ss:alg}, we can easily wrap Alg.~\ref{alg:entropysgd} inside other variants of SGD such as Adam; this involves simply substituting the local entropy gradient in place of the usual back-propagated gradient. For this experiment, we constructed $\entropyadam$ which is equivalent to Adam with the local entropy gradient (which is computed via SGLD). We run $\entropyadam$ for $5$ epochs with $L = 5$ and a fixed $\g = 0.01$ with an initial learning rate of $0.01$ that decreases by a factor of $2$ at each epoch. Note that this again results in only $25$ effective epochs, i.e. half as much wall-clock time as SGD or Adam. We obtain a validation perplexity of $1.213 \pm 0.007$ and a test perplexity of $1.217 \pm 0.005$ over $4$ independent runs which is better than the baseline. Fig.~\ref{fig:char_valid} shows the error curves for this experiment.

@@

After a hyper-parameter search, we obtained a test error on $\lenet$ of $0.63 \pm 0.1\%$ after $300$ epochs and $9.89 \pm 0.11\%$ on $\allcnn$ after $500$ epochs. Even if one were to disregard the slow convergence of SGLD, its generalization error is much worse than our experimental results; we get $0.50 \pm 0.01 \%$ on $\lenet$ and $7.81 \pm 0.09 \%$ on $\allcnn$. For comparison, the authors in~\citet{chen2015bridging} report $0.71\%$ error on MNIST on a slightly larger network.

Our results with local entropy on RNNs are much better than those reported in~\citet{gan2016scalable} for SGLD. On the PTB dataset, we obtain a test perplexity of $77.656 \pm 0.171$ vs. $94.03$ for the same model whereas we obtain a test perplexity of $1.213 \pm 0.007$ vs. $1.3375$ for $\charlstm$ on the War and Peace dataset.

Training deep networks with SGLD, or other more sophisticated MCMC algorithms such as SGHMC, SGNHT etc.~\citep{chen2014stochastic,neal2011mcmc} to errors similar to those of SGD is difficult, and the lack of such results in the literature corroborates our experimental experience. Roughly speaking, local entropy is so effective because it operates on a transformation of the energy landscape that exploits entropic effects. Conventional MCMC techniques such as SGLD or Nose'-Hoover thermostats~\citep{ding2014bayesian} can only trade energy for entropy via the temperature parameter which does not allow the direct use of the geometric information of the energy landscape and does not help with narrow minima.
